|

### 2020-09-15 paper.Rmd

<!-- Add note on interactivity to tuning paragraph. Add a paragraph on applications -->

>>>>

Add note on interactivity to tuning paragraph. Add a paragraph on applications

# Acknowledgements {-}

The authors gratefully acknowledge the support of the Australian Research Council. The paper was written in `rmarkdown` [@rmarkdown] using `knitr` [@knitr].

# Supplementary material {-}

The source material for this paper is available at \url{https://github.com/uschiLaa/burning-sage} XXX rename repo!!!!. The animated gifs for all applications are also included in html files in the supplementary material.
